%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
\newcommand{\matlab}{{\sc Matlab }}
\newcommand{\mixten}{{\sc Mi\xten }}
\newcommand{\xten}{{\sc X10 }}
\newcommand{\discode}{{\sc Discode}}
\documentclass{resume} % Use the custom resume.cls style
\usepackage[hyphens]{url}
\usepackage{hyperref}
%\PassOptionsToPackage{hyphens}{url}\usepackage{hyperref}
\usepackage{setspace} 

%\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage[left=0.5in,top=0.3in,right=0.5in,bottom=0.4in, footskip=0.1in]{geometry} % Document margins
%\usepackage[left=0.2in,top=0.2in,right=1.8in, bottom=0.4in, marginparwidth=1.45in, marginparsep=0.1in, footskip=0.1in]{geometry} % Document margins
\usepackage{marginnote}

\name{Vineet Kumar} % Your name
\begin{document}
\begin{hSubsection}{514-970-9179, vineet.kumar@mail.mcgill.ca}
{%\url{http://vineetkumar.net}
}{3498 Rue Hutchison, Apt\#501, Montreal, QC, Canada - H2X 2G4}
\end{hSubsection}



%----------------------------------------------------------------------------------------
%	SUMMARY SECTION
%----------------------------------------------------------------------------------------
%\marginnote{{\textmd{\textsl{\scriptsize{\hrule Associated with some of the best people, 
%schools and companies in Computer Science      \smallskip\\}}}}}[0.541cm]
\begin{rSection}{Summary}
\smallskip
\begin{lSubsection}
 \item Career interest in \textbf{teaching} and \textbf{research}.
 \item \textbf{M.Sc}, \textbf{McGill University} with research in \textbf{Compilers and Program Analysis \& Transformations} supervised by \textbf{Prof. Laurie Hendren} and assisted by the \textbf{\xten team at IBM Thomas J. Watson Research Center}.
 \item \textbf {Teaching assistantship} for \textbf{two graduate level} courses - Compiler design and  Program analysis \& transformations.
 \item \textbf{3 years} of industry experience in software development as \textbf{Senior Systems Engineer} with \textbf{Infosys Technologies Ltd.}
 \item \textbf{Teaching} and \textbf{technology evangelism} as \textbf{Student Tech Lead, APAC region/Campus Ambassador} (intern) with \textbf{Sun Microsystems}.
 \item \textbf{Co-founder} and \textbf{Student chairman} of GNU Linux and Open Source club of SASTRA University at undergraduate level. 
 \item Experience of working (part-time) with a funded \textbf{e-commerce startup}, developing social network interfaces.
 \item Extensive \textbf{programming experience (C and Java)}.
 \item Experience in all areas of static Compilers including \textbf{program analysis and transformations}, \textbf{compiling dynamic languages} and \textbf{programming language design}.
 
\end{lSubsection}
\end{rSection}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
%\marginnote{{\textmd{\textsl{\scriptsize{\hrule Graduate courses - Compiler Design, 
%Program Analysis and Transformations, Advanced Techniques for Compiling Dynamic Languages, Distributed Systems, Computer Networks, 
%Recommendation Systems for Software Engineering         \smallskip\\
%Active participation in extra-curricular activities     \smallskip\\ 
%}}}}}[0.541cm]
 \begin{rSection}{Education}

\begin{rSubsection}{McGill University}{August 2013 (expected)}{M.Sc. in Computer Science (CGPA: 3.56/4.00)}{Montreal, QC, Canada}
\item Awarded the  \textbf{summer DFW scholarship for top performing} International Graduate students.
\item Gave a grad seminar on \xten and compiling \matlab to \xten.
\end{rSubsection}
\begin{rSubsection}{SASTRA University}{June 2008}{B.Tech. in Computer Science \& Engineering (CGPA: 8.93/10.00)}{Thanjavur, India}
\item For my B.Tech project, I developed \discode: A \textbf{decompiler} targeting C for OpenSolaris on x86.
\item Won the  \textbf{dean's list scholarship for being in the top 10\% }of the University. 
\item \textbf{Co-founded and led} GLOSS(GNU Linux \& Open Source at SASTRA) club of the University.
\item \textbf{Executive member and member of editorial team} of Student Association of School of Computer Science. 
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Publications}
%\begin{rSubsection}{Papers}{}{}{}
\begin{lSubsection}
\smallskip
\item Vineet Kumar and Laurie Hendren. First steps to compiling \matlab to \textsc{X10}.
In Proceedings of the 2013 ACM SIGPLAN X10 Workshop, \textbf{X10 '13} \textbf{co-located with PLDI 2013}.
%\url{http://doi.acm.org/10.1145/2481268.2481273} 
\end{lSubsection}
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
%\marginnote{{\textmd{\textsl{\scriptsize{\hrule  
%Reserach, Teaching, Compilers, Program analysis, Program transformation and optimization techniques, Program language design,Code generation, 
%Java, MATLAB, JastAdd, Flex, Bison, Beaver, \matlab, \xten      \smallskip\\}}}}}[0.541cm]%bad hack but works
\begin{rSection}{Experience}
\begin{rSubsection}{McGill University}{September 2011 - Present}{Research and Teaching}{Montreal, QC, Canada}
\item Research Assistant, \textbf{SABLE Lab} - My research interests include \textbf{program analysis \& transformation techniques} to compile dynamic 
programming languages to static object-oriented and HPC languages. My research is \textbf{supervised by Professor Laurie Hendren}. As a part of my thesis 
I am developing \mixten: a \textbf{\matlab to \xten (A new HPC language by IBM research) compiler}. I get direct assistance 
from the \textbf{\xten team at IBM Thomas J. Watson Research Center}.   
\item Teaching Assistant - COMP 621 Program Analysis and Transformations (Winter 2013). 
\item Teaching Assistant - COMP 520 Compiler Design (Fall 2012).
\end{rSubsection}

%------------------------------------------------
%\marginnote{{\textmd{\textsl{\scriptsize{\hrule 
%Software development, Software engineering, Management, SEO, C, HP LoadRunner        \smallskip\\}}}}}[-0cm]
\begin{rSubsection}{Infosys Technologies Ltd.}{September 2008 - August 2011}{Senior Systems Engineer}{Pune, India}
\item \textbf{Led} the offshore \textbf{deployment performance management} team for AT\&T online and mobility.
\item \textbf{Worked on 8 projects} and they all exceeded performance targets under peak loads.
\item Contributed to the \textbf{SEO recommendation system} used by the \textbf{Infosys global marketing team}.
\end{rSubsection}

%------------------------------------------------
%\marginnote{\textmd{\textsl{\scriptsize{\hrule e-commerce, startup, social network APIs, PHP, Apache, MySQL          \smallskip\\}}}}[0.0cm]
\begin{rSubsection}{MySmartPrice}{October 2010 - July 2011}{Developer (part-time)}{Pune, India}
\item MySmartPrice is an Indian \textbf{e-commerce startup} that provides a price comparison engine for online stores. 
I worked with the founders over weekends and brainstormed design and implementation strategies.
\item I Wrote the initial \textbf{social network interfaces} for facebook and twitter. 
\end{rSubsection}

%\marginnote{\textmd{\textsl{\scriptsize{\hrule Teaching, Evangelism, Open Source culture, OpenSolaris         \smallskip\\}}}}[0.0cm]
\begin{rSubsection}{Sun Microsystems}{January 2007 - May 2008}{Intern - Student Tech Lead, APAC region/Campus Ambassador}{Bangalore, India}
%\item Student Tech Lead/Campus Ambassador, APAC region \\
\item I was promoted from Campus Ambassador to one of \textbf{only 5 Tech Leads worldwide}.
\item Conducted webinars and developed tutorials for Campus Ambassadors worldwide.
%\item Campus Ambassador, India \\
\item As a Campus Ambassador I was one of \textbf{only 27 Campus Ambassadors across India}.
\item \textbf{Taught} a certificate course on \textbf{OpenSolaris}.
\item Conducted several seminars on OpenSolaris and other Sun technologies in SASTRA and nearby Colleges.
\end{rSubsection}
\end{rSection}
\newpage



%----------------------------------------------------------------------------------------
%	SKILLS AND COMPETENCIES SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills and Competencies}
\begin{rSubsection}{Relevant Courses}{}{}{}
\item Compiler Design, Program Analysis \& Transformations, Advanced Techniques for Compiling Dynamic Languages,
Distributed Systems, Computer Networks, Recommendation Systems for Software Engineering.
\end{rSubsection}

\begin{rSubsection}{Programming languages and Software tools}{}{}{}
\item Java, C, PHP, Perl(basic), Javascript(basic), \matlab, \xten, HTML, XML, RSS, twitter API, facebook API, Apache, MySQL, JastAdd, Flex, Bison, Beaver, Eclipse, Vim, \LaTeX. 
\end{rSubsection}

\begin{rSubsection}{Areas of interest (with experience)}{}{}{}
\item Teaching, Research, Software development, Programming language design, Compilers and program analysis, Web startups, Social networking apps, e-commerce.
\end{rSubsection}
\end{rSection}
%\newpage



%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------
%\marginnote{\textmd{\textsl{\scriptsize{\hrule Data flow analysis, Open Source licenses, Compilers, Twitter API, OAuth, RSS, PHP, C, Javascript      \smallskip\\}}}}[0.541cm]
\begin{rSection}{Projects (Course and Other)}
\smallskip
\begin{lSubsection}
    \item isComplex value analysis for \matlab programs: Analysis to identify if a value is complex or real.
    (\href{https://github.com/Sable/mclab/tree/master/languages/Natlab/src/natlab/tame/valueanalysis/components/isComplex}{\em{url}}) 
    \item FreeMeLegal: An Open source license recommendation engine.
    (\href{http://vineetkumar.net/freeMeLegal/free-me-legal_final_report.pdf}{\em{url}})
    \item WIG (a subset of \verb+<+bigwig\verb+>+ language) to PHP compiler (in team of two).
%    \item Performance Analysis and comparison of ZeroMQ and TCP.
%    \item Tweetinawhile: A web-based tweet scheduler.
    \item DotGyan: A server side browser independent search enhancement tool for web pages with textual content.
    (\href{http://vineetkumar.net/dotgyan/}{\em{url}})
%    \item Damruu: A RSS feed reader and chronologically based feed merger.
\end{lSubsection}
\end{rSection}
%\newpage

%----------------------------------------------------------------------------------------
\end{document}
