%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
\newcommand{\matlab}{{\sc Matlab }}
\newcommand{\mixten}{{\sc Mi\xten }}
\newcommand{\mixtenx}{{\sc Mi\xten}}
\newcommand{\xten}{{\sc X10 }}
\newcommand{\xtenb}{{\textbf{\textsc{X10}}}}
\newcommand{\discode}{{\sc Discode}}
\documentclass{resume} % Use the custom resume.cls style
\usepackage[hyphens]{url}
\usepackage{hyperref}
%\PassOptionsToPackage{hyphens}{url}\usepackage{hyperref}
\usepackage{setspace} 

%\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage[left=0.5in,top=0.25in,right=0.5in,bottom=0.2in, footskip=0.0in]{geometry} % Document margins
%\usepackage[left=0.2in,top=0.2in,right=1.8in, bottom=0.4in, marginparwidth=1.45in, marginparsep=0.1in, footskip=0.1in]{geometry} % Document margins
\usepackage{marginnote}

\name{\textsc{Vineet} \textsc{Kumar}} % Your name
\begin{document}
\begin{hSubsection}{514-970-9179, vineet.kumar@mail.mcgill.ca}
{%\url{http://vineetkumar.net}
}{3498 Rue Hutchison, Apt\#501, Montreal, QC, Canada - H2X 2G4}
\end{hSubsection}



%----------------------------------------------------------------------------------------
%SUMMARY SECTION
%----------------------------------------------------------------------------------------
%\marginnote{{\textmd{\textsl{\scriptsize{\hrule Associated with some of the
%best people, schools and companies in Computer Science
%\smallskip\\}}}}}[0.541cm]
\begin{rSection}{Summary} \smallskip \begin{lSubsection} 
\item Seeking a \textbf{full-time} software development position
\textbf{starting May 2014} (or later).  
\item \textbf{M.Sc Computer Science}, McGill University $\vert$
\textbf{3+ years} of \textbf{industry experience} in all aspects of software
development.
\item Extensive programming experience in \textbf{Java} and \textbf{C}.
    %uncomment below if relevant $\vert$ Specialization in compiler design,
    %program analysis and program transformations.
\item Programming languages - \emph{Proficient:} {Java}, {C}, {\xten},
\matlab
$\vert$ \emph{Prior experience:} PHP, Python.
%\item Interests - Compilers, Cloud computing, Recommender systems, Social
%networks, E-commerce, Distributed systems. 
\end{lSubsection}
\end{rSection}

%-----------------------------------------------------------------------------
%	EDUCATION SECTION
%-----------------------------------------------------------------------------
 
\begin{rSection}{Education}

\begin{rSubsection}{McGill University}{April 2014}{M.Sc. in
Computer Science (CGPA: 3.56/4.00)}{Montreal, QC, Canada} 
\item Master's thesis reviewed as \textbf{``Excellent''} by the external
reviewer.
\item Won the {summer differential fee waiver} for being among the
top-performing international students in the University.  
\end{rSubsection}

\begin{rSubsection}{SASTRA University}{June 2008}{B.Tech. in Computer Science
\& Engineering (CGPA: 8.93/10.00)}{Thanjavur, India} 
\item Won the {Dean's list scholarship} for being among the \textbf{top
10\%} students in the University. 
\item \textbf{Co-founded and led} GLOSS(GNU Linux \& Open Source at SASTRA)
club of the University.  
\item \textbf{Executive member} and \textbf{member of the editorial team} of
the Student Association of School of Computer Science. 
\end{rSubsection}

\end{rSection}

%------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%------------------------------------------------------------------------------

\begin{rSection}{Publications and Talks}
\smallskip
\begin{lSubsection}

\item \emph{Publication:} Vineet Kumar and Laurie Hendren. First steps to
compiling \matlab to \xten. In Proceedings of the 2013 ACM SIGPLAN X10
Workshop, \textbf{X10 `13} co-located with \textbf{PLDI
2013}.(\href{http://www.sable.mcgill.ca/mclab/mix10/paper.pdf}{\em{bit.ly/18owBUI}})

\item \emph{Talk:} Vineet Kumar and Laurie Hendren. \mixten: Compiling \matlab
for high performance computing via \xten. 12\textsuperscript{th}
\textbf{Compiler-Driven Performance Workshop} at \textbf{CASCON
2013}.(\href{http://webdocs.cs.ualberta.ca/~amaral/cascon/CDP13/#VinetKumar}{\em{bit.ly/1hXms8N}}) 

\end{lSubsection}
\end{rSection}


%------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%---------------------------------------------------------------------------
\begin{rSection}{Work Experience}

\begin{rSubsection}{McGill University}{January 2012 - April 2014}{Research and
Teaching}{Montreal, QC, Canada} 
\item \textbf{Research Assistant, Sable Lab} - My research included program
analysis and static compilation of dynamic languages.

\begin{lsubSubsection}
  \item Designed and developed (\textbf{in Java}) \mixtenx: a {\matlab to
\xten compiler for high-performance}, under \textbf{Prof.
Laurie Hendren's} supervision and with direct inputs from the \textbf{\xten
design team at the IBM T.J. Watson research
center}.(\href{http://bit.ly/1sZ8aqJ}{\em{bit.ly/1sZ8aqJ}})  
 \item Achieved \textbf{7 times (mean) faster} performance compared to the
 standard \matlab implementation.
  \item Discovered \textbf{2 bugs} and a \textbf{severe performance bottleneck}
in the \xten compiler.  
\end{lsubSubsection}
\item \textbf{Teaching Assistant} - Program Analysis and Transformations,
	Compiler Design, and Introduction to Computer Systems.
\end{rSubsection}

%------------------------------------------------
%\marginnote{{\textmd{\textsl{\scriptsize{\hrule 
%Software development, Software engineering, Management, SEO, C, HP LoadRunner
%\smallskip\\}}}}}[-0cm]
\begin{rSubsection}{Infosys Technologies Ltd.}{September 2008 - August
2011}{Senior Systems Engineer}{Pune, India}
\item \textbf{Led} a team of 4 for \textbf{deployment performance management}
for AT\&T's online and mobility frontend and backend applications.
\begin{lsubSubsection}
\item My team's job was to design and develop (\textbf{in C}) performance
test scripts, analyze results, and troubleshoot performance issues.  
\item {Worked on 8 projects} and they all exceeded performance SLA under
peak loads.
\end{lsubSubsection}
\item Part of the development team for the \textbf{SEO recommendation system} used
by the \textbf{Infosys global marketing team}.  
\end{rSubsection}

%------------------------------------------------
%\marginnote{\textmd{\textsl{\scriptsize{\hrule e-commerce, startup, social
%network APIs, PHP, Apache, MySQL          \smallskip\\}}}}[0.0cm]
\begin{rSubsection}{MySmartPrice}{October 2010 - July 2011}{Developer
(part-time)}{Pune, India} 
\item MySmartPrice is an Indian \textbf{e-commerce startup} that provides a
price comparison engine for online stores. 
\begin{lsubSubsection}
\item Contributed in the design and development of their core crawler algorithm. 
\end{lsubSubsection}
\end{rSubsection}

%\marginnote{\textmd{\textsl{\scriptsize{\hrule Teaching, Evangelism, Open
%Source culture, OpenSolaris         \smallskip\\}}}}[0.0cm]
\begin{rSubsection}{Sun Microsystems}{January 2007 - May 2008}{Intern - Student
Tech Lead, APAC region/Campus Ambassador}{Bangalore, India}
%\item Student Tech Lead/Campus Ambassador, APAC region \\
\item Promoted from being one of the \textbf{only 27 Campus Ambassador across India}
to one of the \textbf{only 5 Tech Leads worldwide}.  
\begin{lsubSubsection}
\item Conducted webinars and developed tutorials for Campus Ambassadors
worldwide.
%\item Campus Ambassador, India \\
%\item As a Campus Ambassador I was one of \textbf{only 27 Campus Ambassadors
%across India}.
\item \textbf{Taught} a certificate course on \textbf{OpenSolaris}.
\end{lsubSubsection}
\end{rSubsection}
\end{rSection}
%\newpage


%----------------------------------------------------------------------------------------
%PROJECTS SECTION TODO discode, distributed systems, networking
%------------------------------------------------------------------------------
\begin{rSection}{Other projects {\MakeLowercase{(top 3)}}}\smallskip \begin{lSubsection}
%SHORTEN top=0.2in TO INCLUDE ANOTHER PROJECT
  
%\item Discode: A decompiler for C on OpenSolaris for intel x86 (B.Tech
%project, individual).(\href{http://vineetkumar.net/discode/}{url -
%\em{bit.ly/15rZr2n}}) 
\item FreeMeLegal: An Open source license recommendation
engine (COMP 762 Recommender systems,
individual).(\href{http://bit.ly/1m030GV}{\em{bit.ly/1m030GV}}) 
\begin{lsubSubsection}
\item Recommendations based on similarities with the top projects on
Sourceforge.net.
\item Implemented a crawler (in {PHP}) to collect data for top projects 
on Sourceforge.net.
\end{lsubSubsection}
%\item WIG (a subset of \verb+<+bigwig\verb+>+ language)
%to PHP compiler (COMP 520 Compiler design, team of two).  
\item Performance
Analysis and comparison of ZeroMQ and TCP (COMP 535 Computer networks, team of
three).(\href{http://bit.ly/1m0dcPE}{\em{bit.ly/1m0dcPE}})  
\begin{lsubSubsection}
\item Compared throughput and latency of a ZeroMQ based P2P chat system to that
of a TCP based P2P chat system.
\item Both the chat systems were implemented by us in Java.
\end{lsubSubsection}

\item Analysis to identify complex numerical values for \matlab programs (COMP
621 Program analysis,
individual).(\href{https://github.com/Sable/mclab/tree/master/languages/Natlab/src/natlab/tame/valueanalysis/components/isComplex}{\em{bit.ly/15SYKmC}}) 
\begin{lsubSubsection}
\item Developed a language to express information propagation through library
function calls.(\href{http://bit.ly/1ezq93q}{\em{bit.ly/1ezq93q}})
\item Accurate results for all the 20 benchmarks used by the 
McLab project.   
\end{lsubSubsection}

%\item A fault-tolerant distributed travel reservation system (COMP 512
%Distributed systems, team of two). 	
%    
%\item TweetInAWhile: A tweet scheduler.
    
%\item DotGyan: A server side browser independent search enhancement tool for
%web pages with textual content
%(personal).(\href{http://vineetkumar.net/dotgyan/}{\em{bit.ly/14FUtBS}})
%    
%\item Damruu: A RSS feed reader and chronologically based feed merger.

\end{lSubsection}
\end{rSection}
%\newpage

%-----------------------------------------------------------------------------
\end{document}
